Illumination Dependency in Dynamic Laser Speckle Analysis

### 2020-02-13 article/article_1.tex
mejorando texto nivel de iluminacion

By the analysis of a piece of paper, as shown in Figs~\ref{fig:illlevel_stdx}, \ref{fig:illlevel_stdy} and \ref{fig:illlevel_stdz};
we can see that the greater the observable laser level of illumination $\mu_p$, 
the greater will be the $\sigma_p$ index of each pixel analysed. 
However, this increase depends on the frequency band in the speckle signal  analysed;
for example, in Fig.~\ref{fig:illlevel_stdz},
with high frequency components, the relation between $\mu_p$ and $\sigma_p$ is almost a horizontal line, 
which means that a variation of $\mu_p$ does not affect significantly the $\sigma_p$ index.
This is reaffirmed by the analysis of the ink drying test, 
seen in Figs~\ref{fig:stdxink}, \ref{fig:stdyink} and \ref{fig:stdzink},
where the curves of regions with high and low luminosity are compared in different frequency bands:
here, the high frequency band  (Fig.~\ref{fig:stdzink}) 
is the one that produces very similar indices, despite the difference in the level of illumination.

>>>>

By the analysis of a piece of paper, as shown in Figs~\ref{fig:illlevel_stdx}, \ref{fig:illlevel_stdy} and \ref{fig:illlevel_stdz};
we can see that the greater the observable laser illumination level $\mu_p$, 
the greater will be the $\sigma_p$ index of each pixel analysed. 
However, this increase depends on the frequency band in the speckle signal  analysed;
for example, in Fig.~\ref{fig:illlevel_stdz},
with high frequency components, the relation between $\mu_p$ and $\sigma_p$ is almost a horizontal line, 
which means that a variation of $\mu_p$ does not affect significantly the $\sigma_p$ index.
This is reaffirmed by the analysis of the ink drying test, 
seen in Figs~\ref{fig:stdxink}, \ref{fig:stdyink} and \ref{fig:stdzink},
where the curves of regions with high and low luminosity are compared in different frequency bands:
here, the high frequency band  (Fig.~\ref{fig:stdzink}) 
is the one that produces very similar indices, despite the difference in the level of illumination.
